### 2021-02-21 newvariant.tex
added a bib file but going to take a break

Since the emergence of the new SARS-CoV-2 variant of concern (VoC), estimating its epidemic strength and speed remains one of the key questions in controlling the spread.
Epidemic strength, characterized by the reproduction number $\RR$, provides information about the final size of the epidemic as well as the amount of intervention required to eliminate the disease.
Epidemic speed, characterized by the growth rate $r$ provides information about the population-level time scale of the epidemic and, therefore, when the new variant will replace the existing variant.
These two quantities are linked by generation intervals---defined as time between infection and transmission---which define individual-level time scale of the epidemic.

>>>>

Since the emergence of the new SARS-CoV-2 variant of concern (VoC), estimating its epidemic strength and speed remains one of the key questions in controlling its spread \citep{davies2021estimated, leung2021early, volz2021transmission}.
Epidemic strength, characterized by the reproduction number $\RR$, provides information about the final size of the epidemic as well as the amount of intervention required to eliminate the disease.
Epidemic speed, characterized by the growth rate $r$ provides information about the population-level time scale of the epidemic and, therefore, when the new variant will replace the existing variant.
These two quantities are linked by generation intervals---defined as time between infection and transmission---which define individual-level time scale of the epidemic.
